Pipit on the Post: Proving Pre- and Post-conditions of Reactive Systems

### 2024-04-02 2024pipit/section/60-Evaluation.tex
eval

\begin{figure}
\begin{minipage}{0.45\textwidth}
\begin{tabbing}
  MM \= MM \= \kill
@let rec@ next ($i$: int) ($c$: cycle): \\
  \> Tot \> (option int) \\
  \>     \> (decreases (count - $i$)) = \\
\>  @if@ trigger_enabled $i$~$c$ \\
\>  @then@ Some $i$ \\
\>  @else if@ $i \ge \text{count} - 1$ \\
\>  @then@ None \\
\>  @else@ next $(i + 1)$~$c$
\end{tabbing}
\end{minipage}
\begin{minipage}{0.55\textwidth}
\begin{verbatim}
  function next(index:  int; c: cycle)
       returns (result: int)
  var next_array: int ^ COUNT;
  let
    next_array[i] =
      if trigger_enabled(COUNT - 1 - i, c)
      then COUNT - 1 - i
      else if i <= 0
      then NO_NEXT_TRIGGER
      else next_array[i - 1];
    result =
      next_array[COUNT - 1 - index];
  tel
\end{verbatim}
\end{minipage}
\caption{Left: next-trigger logic in \fstar{}; right: Kind2 encoding as array scan. In \fstar{}, the \emph{Tot $\tau$ (decreases \ldots)} syntax declares a total function with the given termination measure.
In Kind2, the \tt{int\^{}COUNT} syntax declares an array of integers of length @COUNT@, while the @next_array[i]@ declaration defines the elements of the array as a function of the index @i@.
}
\label{f:evaluation:recursion}
\end{figure}

>>>>

\begin{figure}
\begin{minipage}{0.45\textwidth}
\begin{tabbing}
  MM \= MM \= \kill
@let rec@ next ($i$: int) ($c$: cycle): \\
  \> Tot \> (option int) \\
  \>     \> (decreases (count - $i$)) = \\
\>  @if@ trigger_enabled $i$~$c$ \\
\>  @then@ Some $i$ \\
\>  @else if@ $i \ge \text{count} - 1$ \\
\>  @then@ None \\
\>  @else@ next $(i + 1)$~$c$
\end{tabbing}
\end{minipage}
\begin{minipage}{0.55\textwidth}
\begin{verbatim}
  function next(index:  int; c: cycle)
       returns (result: int)
  var next_array: int ^ COUNT;
  let
    next_array[i] =
      if trigger_enabled(COUNT - 1 - i, c)
      then COUNT - 1 - i
      else if i <= 0
      then NO_NEXT_TRIGGER
      else next_array[i - 1];
    result =
      next_array[COUNT - 1 - index];
  tel
\end{verbatim}
\end{minipage}
\caption{Left: next-trigger logic in \fstar{}; right: Kind2 encoding as array scan. In \fstar{}, the \emph{Tot $\tau$ (decreases \ldots)} syntax declares a total function with the given termination measure.
In Kind2, the \tt{int\^{}COUNT} syntax denotes the type of an array of integers of length @COUNT@, while the @next_array[i]@ declaration defines the elements of the array as a function of the index @i@.
}
\label{f:evaluation:recursion}
\end{figure}
